StreamReduce: Processing Data Streams\\and Avoiding Work

### 2012-05-11 paper/paper.tex
Pretty multiline column header

\subsection{Speed vs. Accuracy Tradeoffs}
\begin{center}
\begin{table*}
  \begin{tabularx}{\linewidth}{|lr|lr|lr|}
    \hline
    \multicolumn{2}{|X|}{Work level = 1.0 and task kill rate = 0.0} &
    \multicolumn{2}{|X|}{Work level = 0.8 and task kill rate = 0.4} &
    \multicolumn{2}{|X|}{Work level = 0.4 and task kill rate = 0.8} \\ \hline
    33225 & title & 21184 & title & 5982 & title \\ \hline
    29356 & web & 18398 & web & 4689 & web \\ \hline
    23095 & book & 13591 & journal & 4225 & journal \\ \hline
    21821 & journal & 13429 & book & 3629 & year \\ \hline
    20124 & year & 12770 & publisher & 3617 & publisher \\ \hline
    19786 & publisher & 12550 & url & 3444 & url \\ \hline
    19478 & url & 12220 & year & 3410 & book \\ \hline
    17360 & news & 11511 & news & 3273 & news \\ \hline
    16685 & accessdate & 11082 & united & 2968 & accessdate \\ \hline
    16401 & united & 10691 & accessdate & 2582 & world \\ \hline
  \end{tabularx}
  \caption{Example top~10 results and their frequencies from several different job
configurations. The top~10 do not change much one changes the parameters to make the job
less accurate.}
  \label{table:top10}
\end{table*}
\end{center}

>>>>

\subsection{Speed vs. Accuracy Tradeoffs}
\begin{center}
\begin{table*}
  \begin{tabularx}{\linewidth}{|lr|lr|lr|}
    \hline
    \multicolumn{2}{|X|}{\begin{tabular}[x]{l}Work level = 1.0 \\ Task kill rate = 0.0\end{tabular}} &
    \multicolumn{2}{|X|}{\begin{tabular}[x]{l}Work level = 0.8 \\ Task kill rate = 0.4\end{tabular}} &
    \multicolumn{2}{|X|}{\begin{tabular}[x]{l}Work level = 0.4 \\ Task kill rate = 0.8\end{tabular}} \\ \hline
    33225 & title & 21184 & title & 5982 & title \\ \hline
    29356 & web & 18398 & web & 4689 & web \\ \hline
    23095 & book & 13591 & journal & 4225 & journal \\ \hline
    21821 & journal & 13429 & book & 3629 & year \\ \hline
    20124 & year & 12770 & publisher & 3617 & publisher \\ \hline
    19786 & publisher & 12550 & url & 3444 & url \\ \hline
    19478 & url & 12220 & year & 3410 & book \\ \hline
    17360 & news & 11511 & news & 3273 & news \\ \hline
    16685 & accessdate & 11082 & united & 2968 & accessdate \\ \hline
    16401 & united & 10691 & accessdate & 2582 & world \\ \hline
  \end{tabularx}
  \caption{Example top~10 results and their frequencies from several different job
configurations. The top~10 do not change much one changes the parameters to make the job
less accurate.}
  \label{table:top10}
\end{table*}
\end{center}
